---
title: "Multiscale GWR"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Multiscale GWR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

In this page we mainly introduce the usage of `gwr_multiscale()`.

```{r setup}
library(sf)
library(GWmodel3)
```

# Basics

Let us set the data `LondonHP` as an example, and show how to use `gwr_multiscale()`.
Assume that the `PURCHASE` is the dependent variable, 
while `FLOORSZ`, `PROF` and `UNEMPLOY` are independent variable, 
we can calibrate a multiscale GWR model with the following code.

```{r model-calibration, cache=T}
data(LondonHP)
m1 <- gwr_multiscale(
  formula = PURCHASE ~ FLOORSZ + UNEMPLOY + PROF,
  data = LondonHP
)
m1
```

Here no additional arguments are set, so the function will apply the follwing configurations:

- No initial value for bandwidth.
- Fixed bandwdith.
- Guassian kernel function.
- Projective coordinate reference system.
- Euclidean distance metrics.
- Centrolized non-intercept independent variables.
- AIC criterion for bandwidth optimization.
- A threshold of $10^{-5}$ for bandwidth optimization.

On most situations, these configurations can ensure the algorithm works.
To further specify arguments, please turn to [Weighting configurations](#weighting-configurations).

This function returns a object of class name `gwrmultiscalem`.
Through the outputs in console,
we can get infromation of fomula, data, kernel, bandwidth, coefficient estimates, and diagnostics.
Besides, it is supported to get more infromation via `coef()` `fitted()` `residuals()`.

```{r coef-fitted-resi}
head(coef(m1))
head(fitted(m1))
head(residuals(m1))
```

In addition, like the old version, `gwrmultiscalem` objects provide a `$SDF` variable 
which contains coefficient estimates and other sample-wise results.

```{r sdf}
head(m1$SDF)
```

We can create maps with this variable.
There is a `plot()` function provided to preview coefficient estimates easily.

```{r plot-model}
plot(m1)
plot(m1, columns = c("FLOORSZ", "UNEMPLOY"))
```

If the second argument is omitted, all coefficient estimates will be mapped by default.
Otherwise, only specified variables will be mapped.

# Weighting configurations

## S4 class for multiscale weighting configrations

This package provides a S4 class named `MGWRConfig`, which is used to set multiscale weighting configurations.
This class contains the following slots:

| Slot              | Type      | Descirption                                                                                                                                                      |
| ----------------- | --------- | ---------------------------------------------------------------------------------------------------------------------------------------------------------------- |
| `bw`              | Numeric   | Bandwidth.                                                                                                                                                       |
| `adaptive`        | Logical   | Whether the bandwidth is adaptive                                                                                                                                |
| `kernel`          | Character | Name of kernel function.                                                                                                                                         |
| `longlat`         | Logical   | Whether coordinates are longitudes and latitudes.                                                                                                                |
| `p`               | Numeric   | The power of Minkowski distance metrics.                                                                                                                         |
| `theta`           | Numeric   | The angle of Minkowski distance metrics.                                                                                                                         |
| `centered`        | Logical   | Whether to centrolize variables.                                                                                                                                 |
| `optim_bw`        | Character | Whether to optimize bandwidth and the criterion's name if yes. Use `"no"` to disable bandwidth optimization; otherwise, set the bandwidth criterion's name here. |
| `optim_threshold` | numeric   | THe threshold of bandwidth optimization.                                                                                                                         |

We can use the function `mgwr_config()` to create an object.

```{r}
mgwr_config(36, TRUE, "bisquare", optim_bw = "AIC")
```

Replicating via `rep()` is enabled, but only the `times` parameter is supported.

```{r}
rep(mgwr_config(36, TRUE, "bisquare", optim_bw = "AIC"), 2)
```

## Use MGWRConfig to configure arguments

The function `gwr_multiscale()` can not only set a uniform configuration,
but also set each a configuration for independent variables.

### Uniform configuration

To set a uniform configuration for all varialbes, just pass a list of only one `MGWRConfig` object.
For example, the following code will set adaptive bandwidth and bi-square kernel for all variables.

```{r, cache=T}
m2 <- gwr_multiscale(
  formula = PURCHASE ~ FLOORSZ + UNEMPLOY + PROF,
  data = LondonHP,
  config = list(mgwr_config(adaptive = TRUE, kernel = "bisquare"))
)
m2
```

Because the default value for `centered` is `TRUE`,
the function will change the value for the intercept to `FALSE` to avoid potential issues at runtime.

Likewise, we can use the `rep()` function, but remember to use a right `times` argument,
which should be equal to the number of independent variables (including the intercept if it exists).

```r
m2 <- gwr_multiscale(
 formula = PURCHASE ~ FLOORSZ + UNEMPLOY + PROF,
 data = LondonHP,
 config = rep(mgwr_config(adaptive = TRUE, kernel = "bisquare"), times = 4)
)
```

### Separate configuration

To set configurations separately for each variable,
we need to input a list of `MGWRConfig` objects
with the same number of elements to that of independent variables (including the intercept if it exists).

```{r, cache=T}
m3 <- gwr_multiscale(
  formula = PURCHASE ~ FLOORSZ + UNEMPLOY + PROF,
  data = LondonHP,
  config = list(
    mgwr_config(bw = 92, adaptive = TRUE, kernel = "bisquare"),
    mgwr_config(bw = 19, adaptive = TRUE, kernel = "bisquare"),
    mgwr_config(bw = 51, adaptive = TRUE, kernel = "bisquare"),
    mgwr_config(bw = 157, adaptive = TRUE, kernel = "bisquare")
  )
)
m3
```

Then the functions `c()` `rep()` can be used to flexiably create such a list.
