---
title: "Geographically Weighted Summary Statistics"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Geographically Weighted Summary Statistics}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(GWmodel3)
```

Geographically Weighted Summary Statistics (GWSS) are some statistics including:

- Average
- Variance
- Standard deviation
- Skewness
- Cross-validation
- Median
- IQR
- QI
- Pearson's correlation
- Spearman's correlation

There are two modes of GWSS: "average" and "correlation".
The Pearson's and Spearman's correlations are available in the "correlation" model,
while others are in the "average" mode.

```{r}
data(LondonHP)
m1 <- gwss(~ PURCHASE + FLOORSZ + UNEMPLOY, LondonHP, 64, TRUE)
m1
m2 <- gwss(~ PURCHASE + FLOORSZ + UNEMPLOY, LondonHP, 64, TRUE, mode = "correlation")
m2
```

And the result is also ready to make plots.

```{r}
plot(m1)
```

