---
title: Basic GWR
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Basic GWR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

In this page we introduce the usage of function `gwr_basic()`.

```{r setup}
library(sf)
library(GWmodel3)
```

# Model Calibration

We use the `LondonHP` data as an example to demonstrate how to use function `gwr_basic()`.
Assume that the `PURCHASE` is the dependent variable, while `FLOORSZ` and `UNEMPLOY` are independent varaibles.
We can build a GWR model through the folloing way.

```{r model-calibration}
data(LondonHP)
m1 <- gwr_basic(
    formula = PURCHASE ~ FLOORSZ + UNEMPLOY + PROF,
    data = LondonHP,
    bw = 64,
    adaptive = TRUE
)
m1
```

Compared with **GWmodel**, the usage is changed in the following ways:

1. The function is renamed to `gwr_basic` to avoid conflicts with the old version.
2. The function no longer support the `regression.points` argument. To predict at new locations, please use the `predict()` function.
3. The OLS part is no longer shown in outputs of the return value. Users can call `lm()` function with specified arguments.

This function return a `gwrm` object.
Through the outputs in console, we can get infromation of fomula, data, kernel, bandwidth, coefficient estimates, and diagnostics.
Besides, it is supported to get more infromation via `coef()` `fitted()` `residuals()`.

```{r}
head(coef(m1))
head(fitted(m1))
head(residuals(m1))
```

In addition, like **GWmodel**, `gwrm` objects provide a `$SDF` variable which contains coefficient estimates and other sample-wise results.

```{r}
head(m1$SDF)
```

We can create maps with this variable. There is a `plot()` function provided to preview coefficient estimates easily.

```{r}
plot(m1)
plot(m1, columns = c("FLOORSZ", "UNEMPLOY"))
```

If the second argument is omitted, all coefficient estimates will be mapped by default.
Otherwise, only specified variables will be mapped.

# Bandwidth Optimization

We can call the function in the following way when we want the function to get an optimized bandwidth instead.

```{r}
data(LondonHP)
m <- gwr_basic(
    formula = PURCHASE ~ FLOORSZ + UNEMPLOY,
    data = LondonHP,
    bw = "AIC",
    adaptive = TRUE
)
message("Bandwidth:", m$args$bw)
```

The method for optimizing bandwidth is specified through strings `"AIC"` or `"CV"`.
Besides, when argument `bw` is missing or set to non-numeric values, this function select an optimized bandwidth according to AIC values.

To obtain the value of optimized bandwidth, use the variable `$args$bw` of the returned object,
or read it from console output.

# Model Selection

In this package, there is a generic function called `model_sel()`.
We we apply it to `gwrm` objects, it can select variables, just like the `stepAIC()` in **MASS**.

```{r}
m2 <- gwr_basic(
    PURCHASE ~ FLOORSZ + UNEMPLOY + PROF + BATH2 + BEDS2 + GARAGE1 +
        TYPEDETCH + TPSEMIDTCH + TYPETRRD + TYPEBNGLW + BLDPWW1 +
        BLDPOSTW + BLD60S + BLD70S + BLD80S + CENTHEAT,
    LondonHP, "AIC", TRUE
)
m2 <- model_sel(m2, criterion = "AIC", threshold = 10, bw = Inf, optim_bw = "AIC")
m2
```

There are two arguments: `bw` and `optim_bw`. This is the way to use them:

1.  When `bw` is missing or is `NA`, then the bandwidth recorded in `gwrm` object is used.
2.  When `bw` is numeric, its value is used in model optimization.
    The value of `optim_bw` determined whether optimize bandwidth again before finally calibrate it.
    - When `optim_bw` is `"no"`, skip the bandwidth optimization process.
    - When `optim_bw` is `"AIC"` or `"CV"`, optimize bandwidth according to the corresponding criterion.
3.  When `bw` is non-numeric, use `Inf` as the bandwidth value to optimize bandwidth.
    And use the criterion specified by `optim_bw` to optimize bandwidth.
    When `optim_bw` is `"no"`, use the AIC criterion by default.

It seems to be complicated, but it is easy to use.
On most occassions, set paramters like the example above.

The returned object after model selection contains a `$model_sel` variable,
in which there are all model combinations and corresponding criterions.
There are three functions to visualize it.

```{r model-sel-vis}
model_sel_view_circle(m2$model_sel, main = "Circle View")
model_sel_view_value(m2$model_sel, main = "AIC Value")
model_sel_view_diff(m2$model_sel, main = "Diff of AIC")
```

We can also use the universal `plot()` function which will make some modification to layouts.

```{r model-sel-plot}
plot(m2$model_sel, main = "Circle View")                 # model_sel_view_circle
plot(m2$model_sel, main = "AIC Value", view = "value")   # model_sel_view_value
plot(m2$model_sel, main = "Diff of AIC", view = "diff")  # model_sel_view_diff
```

If further modification is required, use other arguments supported by `plot()`.

# Predict

Based on the current model, GWR can predict coefficient values at any position.
We can use `predict()` function.

```{r}
predict(m2, LondonHP)
```

The result varies depends on the second argument:

- When it is a `sf` or `sfc` object, the function will return a `sf` or `sfc` object including the orignal geometries.
- When it is a two-column matrix or `data.frame`, the function will return a `data.frame` object without geometries.

Besides, when the second argument is a `sf` or `sfc` object, the returned value varies depends on its attributes:

- When it does not contains all of independent variables, only coefficient estimates will be returned.
- When it only contains all of independent variables, coefficient and dependent variable estimates will be returned.
- When it contains all of independent variables and the dependent variable, coefficient estimates, dependent variable estimates and residuals will be returned.

Then we can get different results for different demands.
