---
title: "GTDR"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{GTDR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Geographically weighted density regression (GTDR), is a model which
calcaulates a wight for each dimension of coordinates,
and calibrate regression model with the product of these weights.
In this page, we mainly introduce the usage of `gtdr()`.

```{r setup}
library(sf)
library(GWmodel3)
```

# Basics

Let us set the data `LondonHP` as an example, and show how to use `gtdr()`.
Assume that the `PURCHASE` is the dependent variable, 
while `FLOORSZ`, `PROF` and `UNEMPLOY` are independent variable, 
we can calibrate a GTDR model with the following code.

```{r model-calibration, cache=T}
data(LondonHP)
m1 <- gtdr(
 formula = PURCHASE ~ FLOORSZ + UNEMPLOY,
 data = LondonHP
)
m1
```

Here no additional arguments are set, so the function will apply the follwing configurations:

- Banwdith size for each dimension is 61.8% samples.
- Adaptive bandwidth for each dimension.
- Gaussian kernel function for each dimension.
- No bandwidth optimization.

On most situations, these configurations can ensure the algorithm works.
To further specify arguments, please turn to [Weighting configurations](#weighting-configurations).

This function returns a object of class name `gtdrm`.
Through the outputs in console,
we can get infromation of fomula, data, kernel, bandwidth, coefficient estimates, and diagnostics.
Besides, it is supported to get more infromation via `coef()` `fitted()` `residuals()`.

```{r coef-fitted-resi}
head(coef(m1))
head(fitted(m1))
head(residuals(m1))
```

Like other functions, `gtdrm` objects provide a `$SDF` variable 
which contains coefficient estimates and other sample-wise results.

```{r sdf}
head(m1$SDF)
```

We can create maps with this variable.
There is a `plot()` function provided to preview coefficient estimates easily.

```{r plot-model}
plot(m1)
plot(m1, columns = c("FLOORSZ", "UNEMPLOY"))
```

If the second argument is omitted, all coefficient estimates will be mapped by default.
Otherwise, only specified variables will be mapped.

# Weighting configurations

## S4 class for dimension-specified weighting configrations

This package provides a S4 class named `GTDRConfig`,
which is used to set dimension-specified weighting configurations.
This class contains the following slots:

| Slot       | Type      | Descirption                        |
| ---------- | --------- | ---------------------------------- |
| `bw`       | Numeric   | Banwdith size.                     |
| `adaptive` | Logical   | Whether the bandwidth is adaptive. |
| `kernel`   | Character | Name of the kernel function.       |

We can use the function `gtdr_config()` to create an object.

```{r}
gtdr_config(0.618, TRUE, "bisquare")
```

Replicating via `rep()` is enabled, but only the `times` parameter is supported.

```{r}
rep(gtdr_config(36, TRUE, "bisquare"), 2)
```

## Use GTDRConfig to configure arguments

The function `gtdr()` can not only set a uniform configuration,
but also set each a configuration for dimensions.

### Uniform configuration

To set a uniform configuration for all dimensions, just pass a list of only one `GTDRConfig` object.
For example, the following code will set the bandwidth size to 10% samples for all dimensions.

```{r, cache=T}
m2 <- gtdr(
 formula = PURCHASE ~ FLOORSZ + UNEMPLOY,
 data = LondonHP,
 config = list(gtdr_config(0.2))
)
m2
```

Likewise, we can use the `rep()` function, but remember to use a right `times` argument,
which should be equal to the number of independent variables (including the intercept if it exists).

```r
m2 <- gtdr(
 formula = PURCHASE ~ FLOORSZ + UNEMPLOY,
 data = LondonHP,
 config = rep(gtdr_config(0.2), times = 2)
)
```

### Separate configuration

To set configurations separately for each dimension,
we need to input a list of `GTDRConfig` objects
with the same number of elements to that of dimensions.

```{r, cache=T}
m3 <- gtdr(
 formula = PURCHASE ~ FLOORSZ + UNEMPLOY,
 data = LondonHP,
 config = list(gtdr_config(bw = 0.5, kernel = "bisquare"),
               gtdr_config(bw = 0.5, kernel = "bisquare"))
)
m3
```

Then the functions `c()` `rep()` can be used to flexiably create such a list.

# Bandwidth Optimization

The bandwidth optimization algorithm for GTDR requires a set of initial values for each parameter.
Thus, even bandwidth optimization is enabled, it is necessary to set the initial values via the `config` argument.
We can enable bandwidth optimization with the following codes.

```{r, cahce=T}
m4 <- gtdr(
    formula = PURCHASE ~ FLOORSZ + UNEMPLOY,
    data = LondonHP,
    optim_bw = "AIC"
)
```

The method for optimizing bandwidth is specified through strings `"AIC"` or `"CV"`.
If the initial values are not appropriate, the function will use the default initial values instead:
61.8% samples for adaptive bandwidth, while 61.8% of maximum distance between samples for fixed bandwidth.

# Model Selection

Apply the `step()` function to `gtdrm` objects to select the best model.
Since version 4.1 of R, the pipe operator `|>` is avaliable.
We can use the following code to enable model selection.

```{r model-selection, eval=FALSE, cache=T, eval=F}
m5 <- gtdr(
    formula = PURCHASE ~ FLOORSZ + UNEMPLOY,
    data = LondonHP,
    optim_bw = "AIC"
) |> step(criterion = "AIC", threshold = 3, optim_bw = "AIC")
```

Where argument `threshold` is the threshold showing minimum changes of the criterion.
Currently, only AIC criterion is supported, so the `criterion` here can only be `"AIC"`.

For R of lower version, please use the following form:

```{r, eval=TRUE}
m5 <- gtdr(
    PURCHASE ~ FLOORSZ + UNEMPLOY,
    LondonHP, optim_bw = "AIC"
)
m5 <- step(m5, criterion = "AIC", threshold = 10, optim_bw = "AIC")
m5
```

We can set `config` in `step()` to overwrite the original configurations.
If it is not set, configurations in the `gtdrm` object will be applied.
Further, if `optim_bw` is sepcified, bandwidth will be optimized afther the model selection.

The returned object after model selection contains a `$step` variable,
in which there are all model combinations and corresponding criterions.
There are three functions to visualize it.

```{r model-selection-view}
step_view_circle(m5$step, main = "Circle View")
step_view_value(m5$step, main = "AIC Value")
step_view_diff(m5$step, main = "Diff of AIC")
```

They are:

1. Variable combinations.
2. Criterions for each combination.
3. Difference of criterions. 
The improvement in the criterion for each combination compared with the previous one is clearly shown.
This figure makes it easier to judge which model meets the requirement.

We can also use the universal `plot()` function which will make some modification to layouts.

```{r model-selection-plot}
plot(m5$step)                  # 等价于 step_view_circle
plot(m5$step, view = "value")  # 等价于 step_view_value
plot(m5$step, view = "diff")   # 等价于 step_view_diff
```

If further modification is required, use other arguments supported by `plot()`.

